\Large \bf \sys: Library-Oriented Program Analysis

### 2020-05-26 paper/draft.tex
Major rewrite

\heading{\sys vs. Jalangi}
For the second experiment, we compare the performance of \sys to that of Jalangi.
Jalangi is a popular dynamic analysis framework for JavaScript;
  it provides fine-grained instrumentation by executing the program using a custom interpreter.
We note our use of Jalangi's v2.2.5 version:
  the v2 branch improves significantly over the performance of the original framework~\cite{jalangi}, as it eschews record/replay capabilities.

In terms of programs, we use Jalangi's extensive test suite.
This is not entirely by choice:
  Jalangi's interaction with the bare-bones libraries was hitting important parsing issues, and was further complicated by \ttt{npm test} (which is an external program outside Node, but tightly coupled with it).
It is important

(Fig.~\ref{fig:meso}).
We compare with and compare \sys's performance to that of Jalangi2.
To be fair in our performance comparison, we design a simple analysis from scratch that both frameworks can express---namely, one for tracking counts of global variable accesses~\sx{impl2}.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

@@

\subsection{End-to-End Benchmarks}
\label{macro}

@@

Finally, we perform end-to-end program dialysis on three large applications:
  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates; and
  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
These applications are highly popular, with Koa.js and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.

@@

\todo{Two types: zooming into prior benchmarks, and targeted micro packages}
\sys's micro-benchmarks were designed to test key properties of each analysis and confirm it outputs the expected results.
For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.
% Each dependency can perform one of three operations, depending on its current state:
%   (i) invoke a call to a module it imports,
%   (ii) busy-wait for a specific amount of time, or
%   (iii) respond to calls by returning a value.
A second goal was to understand \sys's internal overheads in a controlled environment.
% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.

\heading{Sources of Overbred}
To understand the sources of these overheads, we perform a series of micro-benchmarks with tight loops calling several ES-internal libraries without any I/O.
The primary source of overhead seems to be the use of JavaScript's \ttt{with} construct~\sx{}, 
The \ttt{with} construct dominates overheads, as it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards~\cite{}.
% Proxy objects exhibit a much lower cost.
% \TODO{Add some numbers from \ttt{t19} for different configs}.

@@

@@

  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_unique_invalid}
  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_total_invalid}
  \caption{
    \textbf{Access characteristics.}
    \todo{Explain}
  }
  \label{fig:objects}
\end{figure}

\begin{figure}[b!]
  \centering
  \includegraphics[width=\columnwidth]{./figs/lya_n_obj}
  \includegraphics[width=\columnwidth]{./figs/lya_unique_valid}
  % \includegraphics[width=\columnwidth]{./figs/lya_unique_invalid}
  \includegraphics[width=\columnwidth]{./figs/lya_total_valid}
  % \includegraphics[width=\columnwidth]{./figs/lya_total_invalid}
  \caption{
    \textbf{Depth vs. permissiveness.}
    From the top:
    (a) number of \sys wrappers,
    (b) unique valid accesses,
    (c) unique invalid accesses,
    (d) total valid accesses, and
    (e) total invalid accesses---all as a function of \todo{enforcement} depth.
  }
  \label{fig:objects}
\end{figure}

Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of our benchmarks.
The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful.
% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
For example, the ``custom-delay'' benchmark, described earlier, features static bottlenecks across its dependency tree but does not involve interesting access patterns.
The use of \sys adds an overhead that is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
Close inspection confirms that overheads are proportional to the number of wrapped objects and the frequency of accesses:
  most of these benchmarks feature artificially tight loops with high-frequency accesses.
Transformation overheads themselves (not shown in Tab.~\ref{tab:synthetic}) remain under $1ms$.
% is not affected significantly % by transformations altering a library's context

>>>>

\heading{\sys vs. Jalangi}
For the second experiment, we compare the performance of \sys to that of Jalangi.
Jalangi is a popular dynamic analysis framework for JavaScript, providing fine-grained instrumentation by executing on a custom interpreter.
We note our use of Jalangi's v2.2.5 version:
  the v2 branch improves significantly over the performance of the original framework~\cite{jalangi}, as it eschews record/replay capabilities.

In terms of programs, we use Jalangi's extensive test suite within a Jalangi-provided docker container~\cite{jaladocker}
(For these experiments, \sys is also run in the same container.)
This is not entirely by choice:
  Jalangi's interaction with the bare-bones libraries was hitting EcmaScript 6 parsing challenges, further complicated by \ttt{npm test} (which is an external program outside Node, but tightly coupled with it).
Contrary to Jalangi, \sys executes all programs, demonstrating the compatibility benefits of operating on an unmodified runtime.

% FIXME OSDI
% This is an important practical difference with \sys approach:
%   if \sys does not understand, it will simply not wrap it---deferring silently to the default semantics implemented by the runtime rather than

In terms of analysis, both systems are configured to perform dynamic frequency analysis of accesses to global variables.
The analysis is a common denominator between \sys and Jalangi, designed and implemented from scratch to ensure a fair and meaningful comparison between the two frameworks.
Such analyses are useful for understanding how programs with third-party libraries interact with global state---\eg for generating remote-procedure stubs or scaling out functional components~\cite{ignis}.

Fig.~\ref{fig:meso} presents the comparison between \sys and Jalangi.
The core of the analysis requires a few lines, but expressing it in \sys requires 4$\times$ fewer lines of code;
  the effort of employing \sys as a library was also significantly lower than that of Jalangi2, for which we relied on a Docker container to simplify the framework's setup.
The performance results show that \sys performs better than Jalangi2, at times by a significant margin (\ie more than 10$\times$ for 13 benchmarks).
Jalangi2 is more powerful than \sys, capable of expressing analyses that are more fine-grained than \sys's, but results in higher developer effort and runtime performance.

@@

\subsection{Application Benchmarks}
\label{macro}

@@

We perform end-to-end program dialysis on three large applications:
  KoaBlog~\cite{koa}, a minimal blogging platform built on the Koa framework;
  Moeda~\cite{moeda}, a command-line currency converter that, among other features, uses online currency exchange rates; and
  Terminalizer~\cite{terminalizer}, an application for recording terminal sessions to generate animated gif images and shareable web-player links.
These applications are highly popular, with Koa.js and Terminalizer having 28.3K and 8.7K GitHub stars respectively.
Their structural and performance characteristics are shown in Tab.~\ref{tab:macro}.

@@

\sys's micro-benchmarks zoom into \sys's sources of overheads.
%  from \sys and confirm it does not affect the correctness of the program with respect to its sequential execution.
The key results are that
  (i) the majority of the overhead comes from the JavaScript's \ttt{with} expression, which \sys uses to wrap the context of libraries;
  (ii) interposition overhead is negligible in practice;
  (iii) while wrapped and accessed fields increase exponentially as a function of depth (as objects have many fields), object explosion quickly plateaus around level four with under 400 fields; and
  (iv) the majority of wrapped and accessed fields come from Node and EcmaScript names rather than imports or global values.
% We use two broad classes of micro-benchmarks.
% In the first class, we use the same 50 libraries that were the focus of a previous section~\sx{meso} to understand the characteristics of access patterns and \sys-internal overheads in a controlled environment.
% In the second class, we use synthetic micro-benchmarks to test key properties of each analysis and confirm it outputs the expected results.
% For example, to better understand PD and confirm it works correctly, we crafted a micro-benchmark with four dependencies of known static bottlenecks.

% Each dependency can perform one of three operations, depending on its current state:
%   (i) invoke a call to a module it imports,
%   (ii) busy-wait for a specific amount of time, or
%   (iii) respond to calls by returning a value.
% Both of these goals would have been difficult to achieve outside a controlled environment. % , as we do not fully understand applications we haven't written ourselves.

\heading{Sources of Overhead}
To understand the sources of these overheads, we perform a series of micro-benchmarks with tight loops calling several ES-internal libraries without any I/O.
By enabling different parts of \sys, we discover that the primary source of overhead comes from JavaScript's \ttt{with} construct:
  disabling \ttt{with} makes 95\% of the overheads disappear.
The reason \ttt{with} dominates overheads is twofold: it (i) interposes on too many accesses, only a fraction of which are relevant, and (ii) remains significantly unoptimized, since its use is strongly discouraged by the JavaScript standards.
% Proxy objects exhibit a much lower cost.
% \TODO{Add some numbers from \ttt{t19} for different configs}.

@@

\heading{Interposition Overheads}
Table~\ref{tab:synthetic} depicts the results of the three analyses applied to a subset of the aforementioned synthetic benchmarks.
%  (tight loops with no I/O).
The first column indicates the focus of the benchmark; not all analysis--benchmark combinations are useful:
% Currently, these benchmarks return the results we expect, but they did help with the identification of \sys's bugs.
  for example, the ``custom-delay'' benchmark features static bottlenecks across its dependency tree but does not involve interesting access patterns.
\sys-induced slowdown is under 2$\times$, except for the first two cases that feature \emph{only} accesses.
Close inspection confirms a correlation to the number of wrapped objects and the frequency of accesses.
  these benchmarks feature artificially tight loops with high-frequency accesses.
Transformation overheads themselves (not in Tab.~\ref{tab:synthetic}) remain under $1ms$.
% is not affected significantly % by transformations altering a library's context

\heading{Analysis Depth}
To understand the effect of depth in practice, Fig.~\ref{fig:objects} presents the number of wrapped object, unique accesses, and total accesses as a function of depth for all 50 libraries~\sx{meso}.
Depth is explained in the previous paragraph:
   it is about how deep \sys traverses references starting starting from the names in scope---\eg the access \ttt{global.obj.x} is two levels deep and \ttt{fs.readFile} is one level deep.

There are a few highlights worth noting.
While the number of objects wrapped by\sys starts growing exponentially, it quickly reaches an average upper bound of 400 (depending on the exact benchmark).
Accesses grow quickly for the first couple of levels---objects for some of these libraries are hit several thousand times---but then remain stable.
This is usually because most interfaces follow a mostly-flat format where all methods are defined at the top level or right under.

@@

  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_unique_invalid}
  % \includegraphics[width=0.18\textwidth]{./figs/lya_ctx_total_invalid}
  \caption{
    \textbf{Access characteristics as a function of context.}
    Clockwise from top-left:
    (i) number of \sys wrappers,
    (ii) unique valid accesses (\ie counting each access once),
    (iii) total valid accesses~\cf{micro}.
  }
  \label{fig:objects}
\end{figure}

\heading{Context}
Context refers to the broad source of names that are available in the current scope---ones
  defined by the EcmaScript standard (es), 
  through an explicit import (exports),
  by the Node.js runtime (node), or
  via global variables (globs).
A few names seem globally available but are in fact module-locals (\ttt{require}).
User-defined global variables are not prefixed with \ttt{global} thus requiring special interposition (\ttt{with}).

Fig.~\ref{fig:objects} shows \sys's context characteristics on all 50 libraries~\sx{meso}. % as a function of context.
In terms of the number of objects wrapped, the vast majority comes from Node which accounts for 91.1\% of all wrappers.
In terms of unique number of accesses, for both invalid and invalid ones the majority comes from \ttt{require};
  taking their number into account, the majority comes from ES and Node names, whereas the majority of invalid ones comes from \ttt{export}s.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{./figs/lya_n_obj}
  \includegraphics[width=\columnwidth]{./figs/lya_unique_valid}
  % \includegraphics[width=\columnwidth]{./figs/lya_unique_invalid}
  \includegraphics[width=\columnwidth]{./figs/lya_total_valid}
  % \includegraphics[width=\columnwidth]{./figs/lya_total_invalid}
  \caption{
    \textbf{Analysis characteristics as a function of the analysis depth.}
    From the top:
    (i) number of \sys wrappers applied,
    (ii) number of unique accesses (\ie counting each access once),
    (iii) total number of accesses~\cf{micro}.
  }
  \label{fig:objects}
\end{figure}
